An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/intro.tex

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
For example, Yin {\em et al.}~\cite{yin11anempirical} reveal
that about 31\% system failures were caused by misconfiguration problems. 
Misconfigurations, in practice, may result in various
system-wide problems, such as security vulnerabilities, 
application crashes, severe disruptions in software
functionality, and incorrect program executions%
~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.

While many efforts have been proposed 
to check, troubleshoot, diagnose and repair configuration errors%
~\cite{attariyan10automating,
su07autobash, whitaker04configuration}, 
offering automatic verification to configuration files -- like what we
did for verifying regular programs -- is still highly
desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
Nevertheless, the main obstacles to the automatic 
configuration verification are:
1) entries in configuration files are untyped entries, 2) there
is no explicit structure policy for the entries in configuration
files, and 3) there are surprisingly few rules specifying the
entries' constraints.

>>>>

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
For example, Yin {\em et al.}~\cite{yin11anempirical} report
that about 31\% system failures were caused by misconfiguration problems and only 20\% were caused by bugs in program code. 
Misconfigurations, in practice, may result in various
system-wide problems, such as security vulnerabilities, 
application crashes, severe disruptions in software
functionality, and incorrect program executions%
~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.

While many efforts have been proposed 
to check, troubleshoot, diagnose and repair configuration errors%
~\cite{attariyan10automating,
su07autobash, whitaker04configuration},

Ruzica!!!!

they are still not on the level of
automatic verification o

to configuration files -- like what we
did for verifying regular programs -- is still highly
desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
Nevertheless, the main obstacles to the automatic 
configuration verification are:
1) entries in configuration files are untyped entries, 2) there
is no explicit structure policy for the entries in configuration
files, and 3) there are surprisingly few rules specifying the
entries' constraints.
